Papers

### 2023-11-30 quarto/index.qmd
update

**Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
studying language and multimodal models.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained a Ph.D. in Computer Science from University of Illinois Urbana-Champaign.

@@

*<FONT COLOR="#ff0000">I'm hiring</FONT> one Ph.D. research intern at the large language model (Llama) team of Meta GenAI. If you are interested in LLM pre-training and fine-tuning research, just <a href="img/email.png" target="_blank">email me</a>. You'll be working with <a href="https://scholar.google.com/citations?user=SnQnQicAAAAJ" target="_blank">Mike Lewis</a> and me in 2024.*

>>>>

**Aston Zhang** is a research scientist at Meta Generative AI, building large language models (Llama).
Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
studying language and multimodal models.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained a Ph.D. in Computer Science from University of Illinois Urbana-Champaign.

@@

*If you are interested in research internship on large language models at the Llama team in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
